### 2017-10-13 Regeneron Paper.tex
Remove gibberish

	\begin{description}
		\item[buffer] An array that holds a portion of the items in a fragmented list.
		\item[capacity] The maximum amount of items a list can hold without resizing.
		\item[full, filled] A list is full iff its size equals its capacity, meaning it must resize if another item is added.
		\item[growth factor] The factor by which the capacity grows when the list is resized, if the current capacity is nonzero.
		\item[list] The list data type. This term does not refer to a particular implementation of the data type, only the "interface."
		\item[resize] To increase a list's capacity once it is full.
		\item[threshold sizes] The set of sizes for which the list is full.
	\end{description}

@@

	In each "Time Analysis" section, I derive not just the time complexity of the operation, but a complete formula that approximates the actual (amortized) amount of time it takes. In order to do this in a clean fashion, I use the following notation:

	\begin{description}
		\item[$\timeof{F}$] The amortized amount of time it takes for function $F$ to run.
		\item[$T_A$] The amortized amount of time it takes for the code at line to run.
		\item[$T_{A,B}$] The amortized amount of time it takes for code between lines $A$ and $B$ to run, inclusive.
		\item[$T(k)$] The amount of time it takes for $T$ to run, where $T$ is any time expression, when $\size = k$.
		% TODO: T_m should go here?
	\end{description}

	Since the first three definitions represent \textit{amortized} time, which is the average amount of time it takes for an operation to run, I can expand them to

	\begin{align*}
	\timeof{F} &= \frac {\sum_{i = 0}^{n - 1} F(i)} n\\
	T_A &= \frac {\sum_{i = 0}^{n - 1} T_A(i)} n\\
	T_{A,B} &= \frac {\sum_{i = 0}^{n - 1} T_{A,B}(i)} n
	\end{align*}

	% TODO: Where n is an arbitrarily large integer? Since that's true, we may ignore 0 in the below sigmas.

	These definitions will be used frequently when a piece of code takes longer to run for some sizes than others.

	Now, I begin analyzing the amortized amount of time for \addfn. The expression we want to find is \timeof{\addfn}. In order to do this, I will need a few lemmas:

	Lemma. Let \capacities be the set of all values assigned to \capacity as \size increases indefinitely. Let $\capacities(n)$ be the subset of \capacities less than $n$. I show that $capacities(n)$ is the set

	\begin{align*}
	\capacities(n) = \{0\} \cup \{2^i | 1 < i \leq lgc(n) \}
	\end{align*}

	where $lgc(n) = \lfloor \log_2{(n - 1)} \rfloor$, the base 2 \textit{logarithm of the greatest capacity} less than $n$.

	% TODO: Proof

	We define $\overline{\capacities(n)}$ as $\{0, 1, ... n - 1\} \char`\\ \capacities(n)$.

	\begin{align*}
	\timeof{\addfn} &= T_{2,6} = T_2 + T_3 + T_{4,6}\\
	&= T_3 + C\\
	&= \frac {\sum_{i = 0}^n T_3(i)} n + C\\
	&= \frac {\sum_{i \in \capacities(n)} T_3(i) + \sum_{i \in \overline{\capacities(n)}} T_3(i)} n + C
	\end{align*}

	Since $|\capacities(n)| = lgc(n) - 1$ and $|\overline{\capacities(n)}| = n - |\capacities(n)| = n + 1 - lgc(n)$, this resolves to

	\begin{align*}
	\frac {(lgc(n) - 1)\timeof{\resizefn}} n + C
	\end{align*}

	Now we have to determine the complexity of \resizefn.

	\begin{align*}
	\timeof{\resizefn} &= T_{2, 10} = T{6,10}
	\end{align*}

	When $L$ is not full:

	$$
	T_{2,3} + T_{4,6} = \timeof{full?} + T_{4,6} = C
	$$

	When $L$ is full:

	$$
	T_{2,3} + T_{4,6} = \timeof{full?} + T_[resize] + T_{4,6} = T[resize] + C
	$$

	Now we must analyze $resize$.

	When $L$ is empty:

	$$
	T[resize] = T_{2,5} = T[empty?] + T_alloc(4) + T_5 = T_alloc(4) + C
	$$

	When $L$ is non-empty:

	$$
	T[resize] = T[empty?] + 
	$$

>>>>

	\begin{description}
		\item[buffer] An array that holds a portion of the items in a fragmented list.
		\item[capacity] The maximum amount of items a list can hold without resizing.
		\item[full, filled] A list is full iff its size equals its capacity, meaning it must resize if another item is added.
		\item[growth factor] The factor by which the capacity grows when the list is resized, if the current capacity is nonzero.
		\item[list] The list data type. This term does not refer to a particular implementation of the data type, only the "interface."
		\item[resize] To increase a list's capacity once it is full.
		\item[time proportion] The average ratio of the time spent on particular part(s) of a method, to the time spent on the method.
		\item[threshold sizes] The set of sizes for which the list is full.
	\end{description}

@@
